Prediction is Hard (Especially About the Future)

### 2015-08-07 Manuscript.tex
Updates from ShareLaTeX

\subsection{Finding Contrasts}
All the following methods use clustering in the form of WHERE, a top-down clustering method which recursively splits the data in two along a dimension that represents the highest variability, shown as Step-1 in figure \ref{fig:xtrees_bare}. In this work we have explored several algorithms as possible tools used to identify contrast between clusters. These fall into three broad categories: a) Case Based Reasoning techniques (Nearest Neighbors), b) A Gradient base planner (called HOW), and c) Decision Trees.

@@

Our approach is rather straight forward, in that we divide the $N$ training samples into $\sqrt{N}$ clusters and compute the centroid of these clusters. For every test case, we identify a cluster from the training set that most closely resembles it. Following this, we find the nearest cluster with a better performance score. The differences in the attributes between these two clusters constitute the \textit{"contrast set"}. These contrast sets acts as plans that can be used to reflect over the test cases to improve them.

@@

HOW is a very different planner to other CBR systems. HOW

>>>>

\subsection{Finding Contrasts}
All the following methods use clustering in the form of WHERE, a top-down clustering method which recursively splits the data in two along a dimension that represents the highest variability, shown as Step-1 in figure \ref{fig:xtrees_bare}.

In this work we have explored several algorithms as possible tools to identify contrast between clusters. These fall into three broad categories: a) Case Based Reasoning techniques (Nearest Neighbors), b) A Gradient base planner (called HOW), and c) Decision Trees. Each technique offers a distinct advantage over the other.

@@

Our approach is rather straight forward, we divide the $N$ training samples into $\sqrt{N}$ clusters and compute the centroid of these clusters. For every test case, we identify a cluster from the training set that most closely resembles it. Following this, we find the nearest cluster with a better performance score. The differences in the attributes between these two clusters constitute the \textit{"contrast set"}. These contrast sets acts as plans that can be used to reflect over the test cases to improve them.

@@

HOW is very different compared to other CBR planners in that it explores the gradient between pairs of nearby clusters instead of studying the clusters themselves. HOW works by clustering the data during training using WHERE and then drawing \texttt{slopes} between the centroids of pairs of nearby clusters. Assuming the cluster pairs are labeled X and Y, with X having slightly better performance score than Y, the \texttt{slope} between X and Y acts as an indicator pointing to a direction to displace the data; i.e. away from Y and towards X.

While testing, HOW finds the nearest slope to every test case. The slope provides the exact magnitude and direction of displacements. Contrast sets are derived from these displacements. HOW offers a distinct advantage over CBR planners by limiting the displacements to very small regions (the displacements are never more than the separation between two clusters).
